Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-13 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:13	14:03:11	(Thu13.Aug)

In many cases MVDR can improve image contrast and resolution compared to conventional static methods~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}. However, the computational complexity of conventional beamformers are linear with the number of channels, O($M$), while MVDR is at O($M^3$). This may discourage its use and in many cases make it infeasible. We have shown in previous studies that MVDR's complexity can be reduced, as well as accelerated significantly using graphics computing units (GPUs)~\cite{Buskenes2014,Asen2013}, but there is a way to avoid it altogether while achieving similar performance.

This method is called Low Complexity Adaptive (LCA) beamformer and was first proposed by Synnevåg et. al. in clinical medical imaging~\cite{Synnevag2008}, who demonstrated its ability to obtain very similar results to MVDR. It does this by applying a set of predefined windows and selects the one that is best able to suppress noise. Since it uses the same optimisation criterion as MVDR, it may be considered a version of MVDR with a reduced solution space. As we will demonstrate, this works well because MVDR needs

The LCA method was first introduced by Synnevåg et. al. in clinical ultrasound imaging, who demonstrated its ability to improve image quality compared to conventional static beamforming methods \cite{Synnevag2007}.

>>>>

In many cases MVDR can improve image contrast and resolution compared to conventional static methods~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}. However, the computational complexity of conventional beamformers are linear with the number of channels, O($M$), while MVDR is at O($M^3$). This is impracticable and sometimes infeasible. We have shown in previous studies that MVDR's complexity can be reduced, as well as accelerated significantly using graphics computing units (GPUs)~\cite{Buskenes2014,Asen2013}, but there is a way to avoid it altogether while achieving similar performance.

This method is called Low Complexity Adaptive (LCA) beamformer and was first proposed by Synnev\aa{}g et. al. in clinical medical imaging~\cite{Synnevag2008}, who demonstrated its ability to obtain very similar results to MVDR. It does this by applying a set of predefined windows and selects the one that is best able to suppress noise. Since it uses the same optimisation criterion as MVDR, it may be considered a version of MVDR with a reduced window solution space. As we will demonstrate, this works well because a robust MVDR design tend to create windows that resembles slightly varied versions of conventional ones.

This article investigates a few questions that remain unanswered. One is what window functions LCA should be allowed to choose from. This hardly seems to matter,   Our studies show minimal difference between the traditional windows, so the common and reasonable Kaiser-Harris window where the compromize between What windows should the LCA be allowed to choose from? How many is needed?  by Synnev\aa{}g demonstrated the potential of LCA,
